
\documentclass[freya.tex]{subfiles}
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Positions}\descript{}
\location{}
\begin{tabular}{ll}
\heavy{Sept 2015-Current} & Net-A-Porter: Software Developer (Java)\\
\heavy{Jan 2015-July 2015} & Ocado Technology: Senior Software Engineer (Java)\\
\heavy{Aug 2011-Dec 2014} &Ocado Technology: Software Engineer (Java)\\
\heavy{June 2010-Sept 2010} &Marlow Sotfware: Software Developer (Java)\\
\end{tabular}\\
\sectionsep
\runsubsection{Net-A-Porter}
\descript{| Software Developer}
\location{THE OUTNET | September 2015 – Present}
Working as a full stack developer in a small scrum team providing the commerce functionality for THE OUTNET.  This role partly involves maintaining and adapting a large legacy Spring webapp to provide a modern look and feel e-commerce website.  The other side of this role is developing new e-commerce applications in new technologies such as the React JavaScript framework and SpringBoot applications.\\
\sectionsep
\runsubsection{Ocado Technology}
\descript{| Senior Software Engineer}
\location{Marie Claire Launch Squad | February 2015 – July 2015}
Previously worked as Product Owner and Senior Engineer for a cross team squad working on delivering improvements in logistics required for the expansion of the non food side of Ocado's business.  During this period I also championed the setting up of a school leavers apprenticeship scheme.\\
\sectionsep
\location{Geography Systems Team | July 2014 - January 2015}
Focused on developing applications around address management, geo-coding and point to point routing on AWS Cloud infrastructure.   Developed REST Tomcat applications to run on AWS Elastic Beanstalk connecting to various databases including DynamoDB and AngularJS UIs.  During this time I championed the use of TDD, encouraged improved quality and facilitated a few large scale meetings.\\
\sectionsep
\location{Delivery Systems Team | August 2011 - June 2014}
Development of Java applications for Dispatch and Delivery of customer orders (including calculating order price, customer communications and receipts, management of drivers and vans, van based technologies).  Server side, back-end and batch applications developed mainly in Java 7 to connect to Oracle databases or ActiveMQ.  Worked on Stripes based JSPs.  During this time I provided 24/7 support on a rota and mentored interns and new starters.  Re-architected our ActiveMQ installation to reduce single points of failure, and make the system more coherent.  Instigated and developed an automated test harness; continually striving to keep this from becoming obsolete due to regular shifts in our interfaces with other teams.\\


\vspace{5pt}
4 main projects:
\begin{tightemize}
\vspace{5pt}
\item  Launch of Ocado's second warehouse 
 \item Launch of an additional Non-Food Picking Facility and Department Store (Fetch and Sizzle)
 \item Launch of Morrisons' on-line arm on Ocado's infrastructure
 \item Launch of Direct to Spoke allowing significant ramp up of non food sales
 \end{tightemize}
 
\begin{verbose}
\sectionsep
\runsubsection{Marlow Software}
\descript{| Software Engineering Intern}
\location{Summer 2010}
Main developer on a student support application commissioned by an educational psychologist
Interacted with the client, providing information on feasibility of required changes
Demonstrated flexibility working with modifications required by the client, also developing alternate versions\\
\end{verbose}

\end{document}
